Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre

### 2024-10-21 manuscript/manuscript.Rmd
Homogenizing w previous graph by capitalizing SLA

fk_nmdsplot <- nmds_fk$points%*%rot_mat %>%
  as.data.frame() %>%
  setNames(c("MDS1", "MDS2")) %>%
  rownames_to_column("filename") %>%
  left_join(filled_file_metadata %>% distinct(filename, sla_class, depth)) %>%
  mutate(MDS1=MDS1*-1) %>%
  mutate(MDS2=MDS2*-1) %>%
  mutate(fill_col=case_when(
    depth=="Surface" & sla_class=="Cyclone"~"25 m Cyclone",
    depth=="DCM" & sla_class=="Cyclone"~"25 m Anticyclone",
    depth=="Surface" & sla_class=="Anticyclone"~"DCM Cyclone",
    depth=="DCM" & sla_class=="Anticyclone"~"DCM Anticyclone"
  )) %>%
  ggplot(aes(label=filename)) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0) +
  geom_point(aes(x=MDS1, y=MDS2, fill=fill_col, shape=sla_class), size=6, color="white") +
  scale_fill_manual(breaks=c("25 m Cyclone", "25 m Anticyclone", "DCM Cyclone", "DCM Anticyclone"),
                    values=c("#8989c1", "#343489", "#b57c7c", "#762020")) +
  scale_shape_manual(breaks=c("Cyclone", "Anticyclone"), values=c(25, 24)) +
  labs(color="Corr.\nSLA\n(cm)", shape="Depth", x="NMDS axis 1", y="NMDS axis 2") +
  theme_bw() +
  annotate("label", x=-Inf, y=-Inf, hjust=0, vjust=0, label.r = unit(0, "in"),
           label=paste("Stress =", round(nmds_fk$stress, digits = 3))) +
  annotate("label", x=-Inf, y=Inf, hjust=0, vjust=1, label.r = unit(0, "in"),
           label=expression(atop(paste("R"[sla]^2, "=.090, p=0.017"),
                                 paste("R"[depth]^2, "=.251, p<0.001")))) +
  guides(fill=guide_legend(title = NULL, override.aes = list(
    fill=c("#8989c1", "#b57c7c", "#343489", "#762020"), color="white",
    shape=c(25, 24, 25, 24)
  )), shape="none") +
  theme(legend.key.spacing.y = unit(6, "pt")) +
  coord_fixed()

>>>>

fk_nmdsplot <- nmds_fk$points%*%rot_mat %>%
  as.data.frame() %>%
  setNames(c("MDS1", "MDS2")) %>%
  rownames_to_column("filename") %>%
  left_join(filled_file_metadata %>% distinct(filename, sla_class, depth)) %>%
  mutate(MDS1=MDS1*-1) %>%
  mutate(MDS2=MDS2*-1) %>%
  mutate(fill_col=case_when(
    depth=="Surface" & sla_class=="Cyclone"~"25 m Cyclone",
    depth=="DCM" & sla_class=="Cyclone"~"25 m Anticyclone",
    depth=="Surface" & sla_class=="Anticyclone"~"DCM Cyclone",
    depth=="DCM" & sla_class=="Anticyclone"~"DCM Anticyclone"
  )) %>%
  ggplot(aes(label=filename)) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0) +
  geom_point(aes(x=MDS1, y=MDS2, fill=fill_col, shape=sla_class), size=6, color="white") +
  scale_fill_manual(breaks=c("25 m Cyclone", "25 m Anticyclone", "DCM Cyclone", "DCM Anticyclone"),
                    values=c("#8989c1", "#343489", "#b57c7c", "#762020")) +
  scale_shape_manual(breaks=c("Cyclone", "Anticyclone"), values=c(25, 24)) +
  labs(color="Corr.\nSLA\n(cm)", shape="Depth", x="NMDS axis 1", y="NMDS axis 2") +
  theme_bw() +
  annotate("label", x=-Inf, y=-Inf, hjust=0, vjust=0, label.r = unit(0, "in"),
           label=paste("Stress =", round(nmds_fk$stress, digits = 3))) +
  annotate("label", x=-Inf, y=Inf, hjust=0, vjust=1, label.r = unit(0, "in"),
           label=expression(atop(paste("R"[SLA]^2, "=.090, p=0.017"),
                                 paste("R"[depth]^2, "=.251, p<0.001")))) +
  guides(fill=guide_legend(title = NULL, override.aes = list(
    fill=c("#8989c1", "#b57c7c", "#343489", "#762020"), color="white",
    shape=c(25, 24, 25, 24)
  )), shape="none") +
  theme(legend.key.spacing.y = unit(6, "pt")) +
  coord_fixed()
